Non-kissing complexes and tau-tilting for gentle algebras

### 2018-07-13 firstPaper/firstPaperLong/nonKissingComplex.tex
Some referee's changes to first paper.

\begin{proposition}
\label{prop:morphismsStringModules}
Let~$\rho$ and~$\rho'$ be two strings for a string algebra~$A$.
Then the dimension of the $k$-vector space~$\Hom{A} \big( M(\rho), M(\rho') \big)$ is equal to
\[
\sum\limits_{\xi \text{ string}} \begin{array}{l} (\#\textrm{ of substrings equal to~$\xi$ on top of~$\rho$}) \; \cdot \\ \hspace{2cm}(\#\textrm{ of substrings equal to~$\xi$ or~$\xi^{-1}$ at the bottom of~$\rho'$}).\end{array}
\]
\end{proposition}

@@

The following lemma is immediate and left to the reader.
See \fref{fig:exmBlossomingQuiver}.

@@

\begin{remark}
Note that the countercurrent order~$\prec_\alpha$
\begin{itemize}
\item is well-defined: if both endpoints of~$\sigma$ are in~$Q_0$, $\mu_\star$ (resp.~$\nu_\star$) should enter and exit~$\sigma$ in the same direction since~$\mu_\star$ and~$\nu_\star$ are non-kissing;
\item is independent of the orientation of~$\mu_\star$ and~$\nu_\star$:~$\mu_\star \prec_\alpha \nu_\star$ iff $(\mu_\star)^{-1} \prec_\alpha \nu_\star$ iff $\mu_\star \prec_\alpha (\nu_\star)^{-1}$; we thus also consider~$\prec_\alpha$ as a relation on undirected marked walks;
\item depends on which occurrence of~$\alpha$ is marked on~$\mu$ and~$\nu$.
\end{itemize}
\end{remark}

@@

\begin{proof}
We prove that~$\prec_\alpha$ is transitive.
Let~$\lambda_\star$, $\mu_\star$, $\nu_\star$ be three pairwise non-kissing walks marked at an occurrence of~$\alpha$ such that~${\lambda_\star \prec_\alpha \mu_\star \prec_\alpha \nu_\star}$. Let~$v$ be a vertex where~$\lambda_\star$ and~$\mu_\star$ split. Then
%Let~$\sigma$ (resp.~$\tau$, resp.~$\rho$) denote the common substring of~$\lambda_\star$ and~$\mu_\star$ (resp.~of~$\mu_\star$ and~$\nu_\star$, resp.~of~$\lambda_\star$ and~$\nu_\star$) containing that occurrence of~$\alpha$. We distinguish two situations:
\begin{itemize}
\item either~$\nu_\star$ contains~$v$, then it must follow~$\mu_\star$ (otherwise~$\nu_\star \prec_\alpha \mu_\star$), so that~$\lambda_\star \prec_\alpha \nu_\star$.
\item or~$\nu_\star$ does not contain~$v$, then~$\nu_\star$ and~$\mu_\star$ split at a vertex~$w$ between~$\alpha$ and~$v$. Since~${\mu_\star \prec_\alpha \nu_\star}$, $\mu$ (and thus~$\lambda$) leaves~$w$ with an arrow in the same direction as~$\alpha$, while~$\nu$ leaves~$w$ with an arrow opposite to the direction of~$\alpha$, so that~$\lambda_\star \prec_\alpha \nu_\star$.
\end{itemize}
Moreover, $\prec_\alpha$ is antisymmetric by definition.
Finally, any two distinct walks of~$F$ marked at an occurrence of~$\alpha$ are comparable in~$\prec_\alpha$.
Therefore, the reflexive closure of~$\prec_\alpha$ defines a total order on the walks of~$F$ marked at an occurrence of~$\alpha$.
\end{proof}

@@

\begin{definition}
A \defn{join-representation} of~$x \in L$ is a subset~$J \subseteq L$ such that~${x = \bigJoin J}$.
Such a representation is \defn{irredundant} if~$x \ne \bigJoin J'$ for a strict subset~$J' \subsetneq J$.
The irredundant join-representations of an element~$x \in L$ are ordered by containement of the lower ideals of their elements, \ie~$J \le J'$ if and only if for any~$y \in J$ there exists~$y' \in J'$ such that~$y \le y'$ in~$L$.
The \defn{canonical join-representation} of~$x$ is the minimal irredundant join-representation of~$x$ for this order when it exists.
The \defn{canonical meet-representation} is defined dually.
\end{definition}

>>>>

\begin{proposition}
\label{prop:morphismsStringModules}
Let~$\rho$ and~$\rho'$ be two strings for a string algebra~$A$.
Then the dimension of the $k$-vector space~$\Hom{A} \big( M(\rho), M(\rho') \big)$ is equal to the number of pairs~$(\sigma, \sigma')$, where~$\sigma$ and~$\sigma'$ are substrings of~$\rho$ and~$\rho'$, respectively, such that there is an equality of strings~$\sigma' = \sigma^{\pm 1}$.

% \[
% \sum\limits_{\xi \text{ string}} \begin{array}{l} (\#\textrm{ of substrings equal to~$\xi$ on top of~$\rho$}) \; \cdot \\ \hspace{2cm}(\#\textrm{ of substrings equal to~$\xi$ or~$\xi^{-1}$ at the bottom of~$\rho'$}).\end{array}
% \]
\end{proposition}

@@

The following lemma is immediate and left to the reader.
% See \fref{fig:exmBlossomingQuiver}.

@@

\begin{remark}
Note that the countercurrent order~$\prec_\alpha$
\begin{itemize}
\item is well-defined: if both endpoints of~$\sigma$ are in~$Q_0$, then $\mu_\star$ (resp.~$\nu_\star$) enters and exits~$\sigma$ in the same direction since~$\mu_\star$ and~$\nu_\star$ are non-kissing;
\item is independent of the orientation of~$\mu_\star$ and~$\nu_\star$:~$\mu_\star \prec_\alpha \nu_\star$ iff $(\mu_\star)^{-1} \prec_\alpha \nu_\star$ iff $\mu_\star \prec_\alpha (\nu_\star)^{-1}$; we thus also consider~$\prec_\alpha$ as a relation on undirected marked walks;
\item depends on which occurrence of~$\alpha$ is marked on~$\mu$ and~$\nu$.
\end{itemize}
\end{remark}

@@

\begin{proof}
We prove that~$\prec_\alpha$ is transitive.
Let~$\lambda_\star$, $\mu_\star$, $\nu_\star$ be three pairwise non-kissing walks marked at an occurrence of~$\alpha$ such that~${\lambda_\star \prec_\alpha \mu_\star \prec_\alpha \nu_\star}$. Let~$v$ be a vertex where~$\lambda_\star$ and~$\mu_\star$ split. Then
%Let~$\sigma$ (resp.~$\tau$, resp.~$\rho$) denote the common substring of~$\lambda_\star$ and~$\mu_\star$ (resp.~of~$\mu_\star$ and~$\nu_\star$, resp.~of~$\lambda_\star$ and~$\nu_\star$) containing that occurrence of~$\alpha$. We distinguish two situations:
\begin{itemize}
\item either~$\nu_\star$ contains~$v$, then it must leave~$v$ via the same arrow as~$\mu_\star$ (otherwise~$\nu_\star \prec_\alpha \mu_\star$), so that~$\lambda_\star \prec_\alpha \nu_\star$.
\item or~$\nu_\star$ does not contain~$v$, then~$\nu_\star$ and~$\mu_\star$ split at a vertex~$w$ between~$\alpha$ and~$v$. Since~${\mu_\star \prec_\alpha \nu_\star}$, $\mu$ (and thus~$\lambda$) leaves~$w$ with an arrow in the same direction as~$\alpha$, while~$\nu$ leaves~$w$ with an arrow opposite to the direction of~$\alpha$, so that~$\lambda_\star \prec_\alpha \nu_\star$.
\end{itemize}
Moreover, $\prec_\alpha$ is antisymmetric by definition.
Finally, any two distinct walks of~$F$ marked at an occurrence of~$\alpha$ are comparable in~$\prec_\alpha$.
Therefore, the reflexive closure of~$\prec_\alpha$ defines a total order on the walks of~$F$ marked at an occurrence of~$\alpha$.
\end{proof}

@@

\begin{definition}
A \defn{join-representation} of~$x \in L$ is a subset~$J \subseteq L$ such that~${x = \bigJoin J}$.
Such a representation is \defn{irredundant} if~$x \ne \bigJoin J'$ for any strict subset~$J' \subsetneq J$.
The irredundant join-representations of an element~$x \in L$ are ordered by containement of the lower ideals of their elements, \ie~$J \le J'$ if and only if for any~$y \in J$ there exists~$y' \in J'$ such that~$y \le y'$ in~$L$.
The \defn{canonical join-representation} of~$x$ is the minimal irredundant join-representation of~$x$ for this order when it exists.
The \defn{canonical meet-representation} is defined dually.
\end{definition}

### 2018-07-13 firstPaper/firstPaperShort/nonKissingComplex.tex
Some referee's changes to first paper.

\begin{proposition}
\label{prop:morphismsStringModules}
Let~$\rho$ and~$\rho'$ be two strings for a string algebra~$A$.
Then the dimension of the $k$-vector space~$\Hom{A} \big( M(\rho), M(\rho') \big)$ is equal to

\smallskip
\centerline{
\(
\sum\limits_{\xi \text{ string}}  (\#\textrm{ of substrings equal to~$\xi$ on top of~$\rho$}) \cdot  (\#\textrm{ of substrings equal to~$\xi$ or~$\xi^{-1}$ at the bottom of~$\rho'$}).
\)
}
\end{proposition}

@@

The following lemma is immediate and left to the reader.
See \fref{fig:exmBlossomingQuiver} for an example.

@@

\begin{remark}
Note that the countercurrent order~$\prec_\alpha$
\begin{itemize}
\item is well-defined: if both endpoints of~$\sigma$ are in~$Q_0$, $\mu_\star$ (resp.~$\nu_\star$) should enter and exit~$\sigma$ in the same direction since~$\mu_\star$ and~$\nu_\star$ are non-kissing;
\item is independent of the orientation of~$\mu_\star$ and~$\nu_\star$:~${\mu_\star \prec_\alpha \nu_\star \!\iff\! (\mu_\star)^{-1} \prec_\alpha \nu_\star \!\iff\! \mu_\star \prec_\alpha (\nu_\star)^{-1}}$; we thus also consider~$\prec_\alpha$ as a relation on undirected marked walks;
\item depends on which occurrence of~$\alpha$ is marked on~$\mu$ and~$\nu$.
\end{itemize}
\end{remark}

@@

\begin{definition}
A \defn{join-representation} of~$x \in L$ is a subset~$J \subseteq L$ such that~$x = \bigJoin J$.
Such a representation is \defn{irredundant} if~$x \ne \bigJoin J'$ for a strict subset~$J' \subsetneq J$.
The irredundant join-representations of an element~$x \in L$ are ordered by containement of the lower ideals of their elements, \ie~$J \le J'$ if and only if for any~$y \in J$ there exists~$y' \in J'$ such that~$y \le y'$ in~$L$.
The \defn{canonical join-representation} of~$x$ is the minimal irredundant join-representation of~$x$ for this order when it exists.
The \defn{canonical meet-representation} is defined dually.
\end{definition}

>>>>

\begin{proposition}
\label{prop:morphismsStringModules}
Let~$\rho$ and~$\rho'$ be two strings for a string algebra~$A$.
Then the dimension of the $k$-vector space~$\Hom{A} \big( M(\rho), M(\rho') \big)$ is equal to the number of pairs~$(\sigma, \sigma')$, where~$\sigma$ and~$\sigma'$ are substrings of~$\rho$ and~$\rho'$, respectively, such that there is an equality of strings~$\sigma' = \sigma^{\pm 1}$.

% \smallskip
% \centerline{
% \(
% \sum\limits_{\xi \text{ string}}  (\#\textrm{ of substrings equal to~$\xi$ on top of~$\rho$}) \cdot  (\#\textrm{ of substrings equal to~$\xi$ or~$\xi^{-1}$ at the bottom of~$\rho'$}).
% \)
% }
\end{proposition}

@@

The following lemma is immediate and left to the reader.
% See \fref{fig:exmBlossomingQuiver} for an example.

@@

\begin{remark}
Note that the countercurrent order~$\prec_\alpha$
\begin{itemize}
\item is well-defined: if both endpoints of~$\sigma$ are in~$Q_0$, then $\mu_\star$ (resp.~$\nu_\star$) enters and exits~$\sigma$ in the same direction since~$\mu_\star$ and~$\nu_\star$ are non-kissing;
\item is independent of the orientation of~$\mu_\star$ and~$\nu_\star$:~${\mu_\star \prec_\alpha \nu_\star \!\iff\! (\mu_\star)^{-1} \prec_\alpha \nu_\star \!\iff\! \mu_\star \prec_\alpha (\nu_\star)^{-1}}$; we thus also consider~$\prec_\alpha$ as a relation on undirected marked walks;
\item depends on which occurrence of~$\alpha$ is marked on~$\mu$ and~$\nu$.
\end{itemize}
\end{remark}

@@

\begin{definition}
A \defn{join-representation} of~$x \in L$ is a subset~$J \subseteq L$ such that~$x = \bigJoin J$.
Such a representation is \defn{irredundant} if~$x \ne \bigJoin J'$ for any strict subset~$J' \subsetneq J$.
The irredundant join-representations of an element~$x \in L$ are ordered by containement of the lower ideals of their elements, \ie~$J \le J'$ if and only if for any~$y \in J$ there exists~$y' \in J'$ such that~$y \le y'$ in~$L$.
The \defn{canonical join-representation} of~$x$ is the minimal irredundant join-representation of~$x$ for this order when it exists.
The \defn{canonical meet-representation} is defined dually.
\end{definition}
